Summary Tables

### 2019-04-09 summary_tables.Rmd
Fix a conflict and also fix a bug to calculate trip count

@@

## Distance tables
Case study specific duration tables for baseline and five scenarios

>>>>

## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios

```{r load_tidyverse, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```

```{r trip_mode_dist = "asis", echo = F}

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(n() /  u_trips * 100, 2)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

```{r unload_tidyverse, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

@@

## Duration tables
Case study specific duration tables for baseline and five scenarios
